Template for preparing your Brief Report submission to PNAS using Overleaf

### 2023-11-22 PNAS/index.Rnw
Add koehler ref and add newlines in a few paragraphs so it's easier to edit/merge

\Cref{fig:control-overall-fpr} explores the implications of this relationship. The astonishing conclusion is that even at the smallest error rate for striated comparisons, we have about a 3\% chance of at least one false positive conclusion when 10 comparisons are made and about a 37.5\% chance of at least one false positive conclusion when 100 comparisons are made. These results suggest that using current estimates of false positive error rates, it is nearly impossible for wire comparisons to provide compelling, 'beyond a reasonable doubt' levels of evidence.
<<control-overall-fpr, fig.cap="Exploration of overall error rate estimates for different values of $r$, the false positive rate for a single comparison. Dotted vertical lines show false positive error rate estimates (from left to right, \\citep{best2022,bajic2020,mattijssen2021}).", fig.width = 8, fig.height = 4>>=
library(ggplot2)
library(tidyr)
library(dplyr)
library(latex2exp)
library(geomtextpath)
single_rmp = exp(seq(-1000, 0, .1))
N = c(10, 100, 1000, 10000)

@@

If we look at this data differently, we can assess the probability that $N$ comparisons are made accurately (e.g. there are no coincidental matches). It is clear from \Cref{fig:Accuracy} that with existing false positive error rate estimates between 0.07 and 0.0045, the accuracy of the aggregate comparison between a wire and a tool becomes questionable, as the number of candidate alignments that must be examined is too high. Even the most innocuous example we could come up with (small blade, only 2 cutting surfaces, and a relatively large wire) involved a minimum of \Sexpr{2*ncomp_min} completely independent comparisons. As a result, it seems improbable that a wire comparison made under current protocols (with corresponding error rates) would have an overall accuracy rate which would be reliable enough to be presented at trial. When we then consider that examiners would make cuts at multiple angles \citep{baikerToolmarkVariabilityQuality2015}, increasing the number of comparisons even in the simple case we have presented here, the probability of a coincidental match increases

>>>>

\Cref{fig:control-overall-fpr} explores the implications of this relationship.
The astonishing conclusion is that even at the smallest false positive error rate for striated comparisons, we have about a 3\% chance of at least one false positive conclusion when 10 comparisons are made and about a 37.5\% chance of at least one false positive conclusion when 100 comparisons are made.
These results suggest that using current estimates of false positive error rates, it is nearly impossible for wire comparisons to provide compelling, 'beyond a reasonable doubt' levels of evidence.

<<control-overall-fpr, fig.cap="Exploration of overall error rate estimates for different values of $r$, the false positive rate for a single comparison. Dotted vertical lines show false positive error rate estimates (from left to right, \\citep{best2022,bajic2020,mattijssen2021}).", fig.width = 8, fig.height = 4>>=
library(ggplot2)
library(tidyr)
library(dplyr)
library(latex2exp)
library(geomtextpath)
single_rmp = exp(seq(-1000, 0, .1))
N = c(10, 100, 1000, 10000)

@@

If we look at this data differently, we can assess the probability that $N$ comparisons are made accurately (e.g. there are no coincidental matches or examiner errors).
It is clear from \Cref{fig:Accuracy} that with existing false positive error rate estimates between 0.07 and 0.0045, the accuracy of the aggregate comparison between a wire and a tool becomes questionable, as the number of candidate alignments that must be examined is too high.
Even the most innocuous example we could come up with (small blade, only 2 cutting surfaces, and a relatively large wire) involved a minimum of \Sexpr{2*ncomp_min} completely independent comparisons.
As a result, it seems improbable that a wire comparison made under current protocols (with corresponding error rates) would have an overall accuracy rate which would be reliable enough to be presented at trial.
When we then consider that examiners would make cuts at multiple angles \citep{baikerToolmarkVariabilityQuality2015}, increasing the number of comparisons even in the simple case we have presented here, the probability of a coincidental match increases
